Growth Resilience (reanalisis)

### 2017-12-18 analysis/bai/analysis_resilience_bai.Rmd
resilience bai render md

---
title: "Growth Resilience (reanalisis)"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Dec"
output: pdf_document 
bibliography: ../references.bib 
csl: ../ecology.csl
---

>>>>

---
title: "Growth Resilience (reanalisis)"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Dec"
output: 
  md_document:
    variant: markdown_github
bibliography: ../references.bib 
csl: ../ecology.csl
---
